Efficient Coalition Formation \\ for Web Services

### 2013-07-04 papers/coalition-journal-extension/coalition_journal.tex
changes

For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
taxtation method to relax the core condition for more communities to form. 
We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable as number of web services increase and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

One of the properties of coalition structure formation algorithms
in our third scenario is that they partition web services with low
throughput rate so that they usually join coalitions with less
request rate. Since the characteristic function $v(C)$ and the
fair Shapely payoff vector is proportional to web services'
contribution, the web services with small contribution will get
paid much less in communities having web services with high
throughput. On the other hand, according to the valuation function
$v(C)$, web services with high throughput will not contribute well
to communities with low amount of user requests (low market
share). The strong web services are likely to deviate from weak
coalitions, joining a stronger one, which makes the initial
coalition unstable.

>>>>

For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
taxtation method to relax the core condition to help communities, attract web services. 
We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable as number of web services increase and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

One of the properties of coalition structure formation algorithms
in our second scenario is that they partition web services with low
throughput rate so that they usually join coalitions with less
request rate. Since the characteristic function $v(C)$ and the
fair Shapely payoff vector is proportional to web services'
contribution, the web services with small contribution will get
paid much less in communities having web services with high
throughput. On the other hand, according to the valuation function
$v(C)$, web services with high throughput will not contribute well
to communities with low amount of user requests (low market
share). The strong web services are likely to deviate from weak
coalitions, joining a stronger one, which makes the initial
coalition unstable.
